Multisensor Architecture for an Intersection Management System

### 2019-01-22 ch3-arch_sys.tex
Fixed JSON definition

Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options. This information is loaded into Redis from a JSON file and it is available for any client requiring it.
\todo{Define JSON HERE!!!!}

@@

\todo{Move JSON definition from here!!!}
Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JavaScript Object Notation (JSON), allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.

>>>>

Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options. This information is loaded into Redis from a configuration file formatted using JavaScript Object Notation (JSON), available for any client requiring it.
\todo{Define JSON HERE!!!!}

@@

\todo{Move JSON definition from here!!!}
Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JSON, allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.
